### 2018-07-26 thesis/2_chapters/chap4.tex
thesis submitted

\begin{ntutab}{|c|c|}{environment}{Environment condition}
    \hline
    \textbf{Condition} & \textbf{value} \\
    \hline
    Ambient temperature &  \\
    \hline
    Airflow & 250 LFM \\
    \hline
    heat sink & medium \\
    \hline
    board temperature & $25.0^oC$ \\
    \hline
\end{ntutab}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 4.2
\section{Runtime experiments}

>>>>

The power consumption of the design is measured based on the condition described in Table~\ref{tab:environment}.

\begin{ntutab}{|c|c|}{environment}{Environment condition}
    \hline
    \textbf{Condition} & \textbf{value} \\
    \hline
    Ambient temperature & $30.0^oC$ \\
    \hline
    Airflow & 250 LFM \\
    \hline
    heat sink & medium \\
    \hline
    board temperature & $25.0^oC$ \\
    \hline
\end{ntutab}

\noindent As in Figure~\ref{fig:power_sum} and Figure~\ref{fig:power}, the Processing System(the ARM A9 processor) consumes 77\% of the power supplied while other hardware components like the IP core, BRAM consume less power. This is due to the fact that generic processors are designed for multiple purpose tasks; hence they are not optimal for power consumption as the hardware solution for a specific task.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 4.2
\newpage
\section{Runtime experiments}

### 2018-07-26 thesis/2_chapters/chap5.tex
thesis submitted

% Chapter 5
\chapter{Conclusion and Future Works}
\label{chap:conclusion}

@@

\section{Conclusion}

@@

>>>>

% Chapter 5
\chapter{Summary and Future Works}
\label{chap:conclusion}

@@

@@

Currently, the system can not handle a high throughput image data streaming. In my experiments, I have to handle the images one-by-one to feed into the system. Hence, I suggest implementing an input-processing module with can manage a large stream amount of image data(around 9.8 GBs) autonomously. \\

\noindent Moreover, the first dataset is generated by sky simulation with slightly normal distribution noise added, the second dataset is captured by a star tracker from the ground. In space, there are more noises affect the quality of the images from the electromagnetic field, Solar noise, Cosmic noise, etc. A noise cancellation module implemented in the PL would be needed.
